---
title: "Variation Stuff"
output: html_notebook
---

Load the datasets:

```{r}
reaches <- read.csv('data/variation_reaches.csv', stringsAsFactors = F)
localizations <- read.csv('data/variation_localizations.csv', stringsAsFactors = F)
error.clamp.idx <- which(reaches$distortion == 360)
reaches$distortion[error.clamp.idx] <- NA
localizations$distortion[error.clamp.idx] <- NA
```

First we care mostly about the localizations. Just to be sure we baseline it first. (Doesn't seem to matter much...)

```{r}
baseline <- function(reachvector,blidx) reachvector - mean(reachvector[blidx], na.rm=TRUE)
localizations[,2:ncol(localizations)] <- apply(localizations[,2:ncol(localizations)], FUN=baseline, MARGIN=c(2), blidx=c(24:49))
```

Let's get the mean and a confidence interval for every trial:

```{r}
mu <- apply(localizations[2:33], MARGIN=c(1), FUN=mean, na.rm=TRUE)
plot(mu, type='l')
```

Now, we scale it by the distortion:

```{r}
plot(c(1:length(mu)-51), mu / localizations$distortion, type='l')
```

This looks like a decreasing line: the proportion does decrease when people experience a lot of changes in the distortion. Is it significant?

```{r}
timeProp <- data.frame('trial'=c(1:length(mu))-51, 'proportion'=mu/localizations$distortion)
# timeProp <- timeProp[which(localizations$distortion != 0),]  # division by 0 also results in infinite proportions:
timeProp <- timeProp[is.finite(timeProp$proportion),]
linearPropModel <- lm(proportion ~ trial, data=timeProp)
summary(linearPropModel)
```

So trial (time) explains part of the proportion: localization/rotation. Let's look at the intercept at the first rotated trial:

```{r}
plot(-1000,-1000,main='proportion over time',xlab='rotated trial',ylab='proportion',xlim=c(0,430),ylim=c(-.4,+.8),bty='n')

lines(c(0,430),c(0,0))

predicted <- predict(linearPropModel, newdata = data.frame('trial'=c(1:length(mu))), interval='confidence')
n <- dim(predicted)[1]

lines(c(51,length(mu))-51,c(0.2,0.2),col='blue',lty=2)

polygon(x=c(c(51:n)-50,rev(c(51:n)-50)), y=c(predicted[c(51:length(mu)),2], rev(predicted[c(51:length(mu)),3])), col="#ff00ff2f", border=NA)

lines(x=c(51:n)-50, y=predicted[c(51:length(mu)),1], col='#ff00ff')

lines(c(1:length(mu)-51), mu / localizations$distortion, type='l', col='red')
```

Let's look at the immediacy of shifts in localization responses across variations. First we detect where the rotation changes are.

```{r}
rotchanges <- which(diff(localizations$distortion) != 0) + 1
diff(rotchanges)
```

So that's mostly every 12 trials, but all changes from a rotation to itself (including from error-clamped to error-clamped I think) are there as well (those are the 24 trial epochs). However, we'll look at the localization deviation on the rotation change trials, and compare them to trials 9-12 after that (all 4 targets). 

```{r}

plot(localizations$distortion, type='l', col='gray')

for (rotchange.idx in rotchanges) {
  
  initial_localization <- mu[rotchange.idx+1]
  
  if (localizations$distortion[rotchange.idx+1] == 0) next() # skip shifting to 0?
  
  # confidence interval needs to have all participants responses to be reliable?
  # let's assume normality, so we don't bootstrap:
  
  data <- as.vector(as.matrix(localizations[c((rotchange.idx+9):(rotchange.idx+12)),c(2:33)]))
  data <- colMeans( localizations[c((rotchange.idx+9):(rotchange.idx+12)),c(2:33)], na.rm=TRUE )
  data <- data[is.finite(data)]
  #print(data)
  
  cat(sprintf('\ntrial: %d, rotation: %d, (change: %d)  \n',rotchange.idx+1, localizations$distortion[rotchange.idx+1], diff(localizations$distortion[c((rotchange.idx-1):(rotchange.idx))])))
  CI <- SMCL::getConfidenceInterval(data=data)
  cat(sprintf('CI: low %0.4f  hi %0.4f\n',CI[1], CI[2]))
  for (trialadd in c(1:4)) {
    if (mu[rotchange.idx+trialadd] > min(CI) & mu[rotchange.idx+trialadd] < max(CI)) {
      cat(sprintf('WITHIN: trial %d: localization: %0.4f\n', trialadd, mu[rotchange.idx+trialadd]))
    } else {
      cat(sprintf('OUTSIDE: trial %d: localization: %0.4f\n', trialadd, mu[rotchange.idx+trialadd]))
    }
  }

}
```




